\printglossary
\clearpage

GLOSSARY ENTRIES
\newglossaryentry{LABEL}
{
  name=NAME,
  description={DESCRIPTION}
}
**name is usually lower case and can have spaces
**label should not have spaces
**just follow the examples

\newglossaryentry{time-reversal}
{
    name=time reversal,
    description={Time-reversal can refer to $(1)$ the property of time reversal symmetry in the system; or $(2)$ the signal focusing technique. \(In this thesis, the abreviation TR will refer to \(2\)\)}
}
\newglossaryentry{pulse-inversion}
{
   name=pulse inversion,
  description={The signal processing technique for isolating the nonlinear component of a signal.}
}
\newglossaryentry{efficiency}
{
   name=efficiency,
  description={TODO}
}
\newglossaryentry{range}
{
   name=range,
  description={Range is defined here as the maximum distance that a given amount of power can be transmitted.}
}
\newglossaryentry{max-power}
{
   name=maximum power,
  description={The maximum amount of power that can be transmitted to a target using a given technology.}
}
\newglossaryentry{active-transmission}
{
   name=active transmission,
  description={An active technique is one in which the receiver requires power.}
}
\newglossaryentry{passive-transmission}
{
   name=passive transmission,
  description={A passive technique is one in which the receiver does not require power.}
}
\newglossaryentry{transmitter}
{
   name=transmitter,
  description={The component of the TRM that broadcasts the interogation pulse.}
}
\newglossaryentry{receiver}
{
   name=receiver,
  description={The component of the TRM that receives the reconstruction.}
}
\newglossaryentry{impedance-matching}
{
   name=impedance matching,
  description={The method of adapting the the impedance of a load to the impedance of a power source such that power delivered to the load is maximized.}
}
\newglossaryentry{reverberant}
{
   name=reverberant,
  description={}
}
\newglossaryentry{sona}
{
   name=sona,
  description={Sona: originating from sonabilis, resonant, is a signal recovered at the receiver during the interrogation stage of the TR process. The sona signal is time reveresed, and injected to form a reconstruction at the desired receiver.}
}
\newglossaryentry{reconstruction}
{
   name=reconstruction,
  description={A desired focused signal produced at a desired receiver. Reconstuctions are formed from the injection of time-reversed sona at the transmitter.}
}
\newglossaryentry{collapse}
{
   name=collapse,
  description={TODO}
}
\newglossaryentry{scatterer}
{
   name=scatterer,
  description={An element that functions to isotropically scatter ambient waves.}
}
\newglossaryentry{heterogeneous-medium}
{
   name=heterogeneous medium,
  description={TODO}
}
\newglossaryentry{homogenous-medium}
{
   name=homogenous medium,
  description={TODO}
}
\newglossaryentry{anisotropic-scatterer}
{
   name=anisotropic scatterer,
  description={A scattering element with a directional bias.}
}
\newglossaryentry{port}
{
   name=port,
  description={An electrical facet of our cavity for forming an electrical network.}
}
\newglossaryentry{gigabox}
{
   name=Gigabox,
  description={The microwave cavity used for our experimental TRM.}
}
\newglossaryentry{interrogation-pulse}
{
   name=interrogation pulse,
  description={The signal injected at the transmitter in order to obtain desired sona at the receiver.}
}
\newglossaryentry{mode}
{
   name=mode,
  description={An eigenfunction of the wave equation given the boundary conditions of a system.}
}
\newglossaryentry{carrier-frequency}
{
   name=carrier frequency,
  description={The frequency of the carrier wave for our interrogation process.}
}
\newglossaryentry{linear-tr}
{
   name=linear time reversal,
  description={TODO}
}
\newglossaryentry{nonlinear-tr}
{
   name=nonlinear time reversal,
  description={TODO}
}
\newglossaryentry{s-parameters}
{
   name=S parameters,
  description={The parameters of a scattering matrix which describe a linear electronic networks.}
}
\newglossaryentry{injecting-port}
{
   name=injecting port,
  description={A port designated for broadcasting (injecting) signals.}
}
\newglossaryentry{recording-port}
{
   name=recording port,
  description={A port designated for recording broadcasts injected into the cavity.}
}
\newglossaryentry{parasitic-capacitance}
{
   name=parasitic capacitance,
  description={The unwanted capacitance introduced from the arrangement of components in an electrical network along with materials.}
}
\newglossaryentry{reverse-conductance}
{
   name=reverse conductance,
  description={TODO}
}
\newglossaryentry{knee-voltage}
{
   name=knee voltage,
  description={The voltage nescessary for "turning on" a diode.}
}
\newglossaryentry{mode-density}
{
   name=mode density,
  description={A discription of the seperation of modes in terms of frequency (energy) separation; as $\delta f = 0$ the mode spectrum tends to form a continuum.}
}
\newglossaryentry{ray-chaotic-environment}
{
   name=ray chaotic environment,
  description={An important feature of a chaotic system where there is a sensitive dependence on initial conditions; if one were to consider two ray originating at a given point with an arbitrarily small angle in separation, the forward ray traces quickly diverge. For our application, the implication is these ray traces will cover the volume of the cavity.}
}
\newglossaryentry{short-orbit}
{
   name=short-orbit,
  description={The mechanism responsible for the multiple reconstruction signals appearing at different time intervals. }
}
\newglossaryentry{}
{
   name=,
  description={TODO}
}








ACRONYMS
\newacronym{LABEL}{ABBREVIATION}{EXPANDED}
**Labels cannot be repeated, including glossary labels
**Label is usually just lower-case form of the abbreviation

\newacronym{wpt}{WPT}{Wireless Power Transfer}
\newacronym{tr}{TR}(Time Reversal)
\newacronym{nltr}{NLTR}{Nonlinear Time Reversal}
\newacronym{pwm}{PWM}{Pulse Width Modulation}
\newacronym{fft}{FFT}{Fast Fourier Transform}
\newacronym{cst}{CST}{Computer Simulation Technology}
\newacronym{hrmc}{HRMC}{Highly Resonant Magnetic Coupling}
\newacronym{trm}{TRM}{Time Reversal Mirror}
\newacronym{dort}{DORT}{Decomposition of the Time Reversal Operator}
\newacronym{ltr}{LTR}{Linear Time Reversal}
\newacronym{awg}{AWG}{Arbitrary Waveform Generator}
\newacronym{psg}{PSG}{Pulse Signal Generator}
\newacronym{dso}{DSO}{Digital Storage Oscilloscope}
\newacronym{fft}{FFT}{Fast Fourier Transform}
\newacronym{cnam}{CNAM}{Center for Nanophysics and Advanced Materials}
\newacronym{em}{EM}{Electromagnetic}
\newacronym{cst}{CST}{Computer Simulation Technology: Microwave Studio}
\newacronym{fit}{FIT}{Finite Integration Technique}
\newacronym{fdtd}{FDTD}{Finite Difference Time Domain}
\newacronym{pwm}{PWM}{Pulse Width Modulation}
\newacronym{trr}{TRR}{Reverse Recovery Time}
\newacronym{rf}{RF}{Radio Frequency}



\printglossary[type=\acronymtype]
\clearpage
\newpage
